Article Title

### 2013-10-22 sections/Estimators.tex
updated figure 5.

Factor analysis has long been used to test hypotheses about the dominance of a few common inputs \cite{findagoodone}.  In neuroscience, the hypothesis that the population activity in small local circuits is largely driven by a few latent factors has been investigated \cite{Yu:2009,Ecker:2013}.  Estimation of covariance matrices by shrinkage toward a factor model has been used in finance for portfolio risk assessment \cite{Ledoit:2003,Fan:2008}.

@@

For Gaussian Graphical Models, zeros in the inverse covariance matrix indicate statistical independence between the corresponding pairs. Thus the inverse covariance matrix $S=-\Sigma^{-1}$ is also the adjacency matrix of the GGM, indicating which pairs are conditionally dependent. \TODO{discuss how quickly (or slowly) this breaks down with deviations from gaussianity, e.g.~MaxEnt models, Ising models.} \TODO{Also, motivate this from the perpsective of linear regression as in \cite{Varoquaux:2012}.}  \Kcomment{This is a bit confusing -- in the first sentence, you have statistical independence, in the second, you talk about conditional independence.  You want to emphasize that a 0 inverse means that -- in the GGM -- the two nodes only ``talk'' indirectly through other nodes.} The off-diagonal elements of $S$ are proportional to partial pairwise correlations between corresponding pairs of neurons. \TODO{Expand.} Regularization of covariance matrix estimation by sparsifying the inverse of the estimate has been using in function genomics \cite{Schafer:2005,other} and fMRI functional connectivity \cite{Varoquaux:2012}.

>>>>

Factor analysis has long been used in natural sciences to infer the influence of a one or several latent variables exerting linear effects on a larger population of observed variables \cite{Jvreskog:1996}.  In neuroscience, the hypothesis that the population activity in small local circuits is largely driven by a few latent factors has been investigated \cite{Yu:2009,Ecker:2013}.  Estimation of covariance matrices by shrinkage toward a factor model has been used in finance for portfolio risk assessment \cite{Ledoit:2003,Fan:2008}.

@@

For Gaussian Graphical Models, zeros in the inverse covariance matrix indicate statistical independence between the corresponding pairs. Thus the inverse covariance matrix $S=-\Sigma^{-1}$ is also the adjacency matrix of the GGM, indicating which pairs are conditionally dependent. \TODO{discuss how quickly (or slowly) this breaks down with deviations from gaussianity, e.g.~MaxEnt models, Ising models.} \TODO{Also, motivate this from the perpsective of linear regression as in \cite{Varoquaux:2012}.}  \Kcomment{This is a bit confusing -- in the first sentence, you have statistical independence, in the second, you talk about conditional independence.  You want to emphasize that a 0 inverse means that -- in the GGM -- the two nodes only ``talk'' indirectly through other nodes.} The off-diagonal elements of $S$ are proportional to partial pairwise correlations between corresponding pairs of neurons. \TODO{Expand.} Regularization of covariance matrix estimation by sparsifying the inverse of the estimate has been using in functional genomics \cite{Schafer:2005,Peng:2009} and fMRI functional connectivity \cite{Varoquaux:2012,Ryali:2012}.

### 2013-10-22 sections/Figure1.tex
updated figure 5.

\begin{figure}[htp]
\begin{center}
\includegraphics[width=2.5in]{figures/Figure1.pdf}
\end{center}
\caption{
{\bf Acquistion of neural population activity using two-photon fluorescence imaging of calcium signal.}  {\bf A.} Visual stimuli comprising brief (500 ms) presentatios of full-field drifting gratings separated by blank screens. {\bf B.} Two-photon fast 3D imaging of calcium signals in an awake mouse. {\bf C.} Deconvolved calcium signals. {\bf D.} The sample covariance matrix of neuronal calcium signals in 200 ms time bins. 
}
\label{Figure_label}
\end{figure}

>>>>

\begin{figure}[htp]
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/Figure1.pdf}
\end{center}
\caption{
{\bf Acquistion of neural population activity using two-photon fluorescence imaging of calcium signal.}  {\bf A.} Visual stimuli comprising brief (500 ms) presentatios of full-field drifting gratings separated by blank screens. {\bf B.} Two-photon fast 3D imaging of calcium signals. {\bf C.} The first and last 30 seconds of a 30-minute recording of population calcium signals. The signals are deconvovled and binned at 150 ms. {\bf D.} The sample noise correlation matrix of neuronal calcium signals from {\bf C} after subtracting the average stimulus response. {\bf E.} The hIstogram of off-diagonal coefficients from the correlation matrix in {\bf D}.
}
\label{fig:01}
\end{figure}

### 2013-10-22 sections/Figure5.tex
updated figure 5.

\begin{figure}[htp]
\centering
\includegraphics[width=1.0\textwidth]{figures/Figure5.pdf}
\caption{
Example of covariance structure revealed by the sparse+low-rank estimator and its relationship to the circuit arcitecture.
}
\label{fig:05}
\end{figure}

>>>>

\begin{figure}[htp]
\centering
\includegraphics[width=0.5\textwidth]{figures/Figure5.pdf}
\caption{
Example of covariance structure revealed by the sparse+low-rank estimator and its relationship to the circuit arcitecture.
{\bf A:} The correlation matrix from Fig.~\ref{fig:01}D. 
{\bf B:} Optimal cross-validated sparse+low-rank estimate of the corrleation matrix from the same dataset. 
{\bf C:} Scaled negative inverse of the correlation matrix in {\bf A} (partial pairwise correlations). 
{\bf D:} Negative inverse of the sparse+low-rank estimate in {\bf B}. 
{\bf E:} The sparse component of {\bf D} with 96.5\% off-diagonal coefficients set to zero.
{\bf F:} The low-rank component of {\bf D}, rank=7.
{\bf G:} The spatial arrangement of cells used in the analysis, connected by edges that correspond to the non-zero elements of the sparse component in {\bf E}. Green edges denote positive weights, red edges denote negative weights.  Color-filled cells are significantly tuned to grating orientation as indicated by the color code in the legend.
}
\label{fig:05}
\end{figure}
